"\\chapter{INTRODUCTION}\n\\rule{\\textwidth}{1pt}\n\\paragraph{}\n\\section{INTRODUCTION}\n\nThe rapid digitization of higher education has fundamentally altered how students access, generate, and share academic knowledge. Engineering students today produce an enormous volume of academic content --- handwritten notes, solved assignments, previous year question papers, project reports, and code snippets --- yet continue to rely on fragmented, insecure, and unstructured channels such as WhatsApp groups, Google Drive links, and Telegram chats to distribute this content among peers. These informal methods, while convenient, suffer from severe limitations: files are lost, links expire, content goes unverified, and there is no mechanism to reward quality contributions or guide students toward meaningful career outcomes.\n\\vspace{0.5cm}\n\n\\textbf{NoteHub} is a next-generation, AI-augmented academic knowledge-sharing ecosystem engineered to address these exact challenges. It is a full-stack, cross-platform solution that unifies a \\textbf{React.js web application} and a \\textbf{React Native mobile application} (built with Expo) under a shared \\textbf{Node.js/Express.js} backend and a \\textbf{PostgreSQL} relational database. The platform is deployed on cloud infrastructure using Docker containers with Vercel for the frontend and Render for the backend, ensuring high availability and scalability.\n\\vspace{0.5cm}\n\nAt its core, NoteHub goes far beyond a simple file-sharing tool. It incorporates a \\textbf{multi-layer plagiarism detection engine} --- combining the Winnowing algorithm, sentence-level TF-IDF analysis, SimHash fingerprinting, and live web-source crawling --- to ensure that every document published on the platform is original and academically credible. An \\textbf{AI-powered Career Advisor} --- driven by Google Gemini 2.0 Flash with a Retrieval-Augmented Generation (RAG) pipeline --- provides students with personalized, curriculum-aware career roadmaps and skill-building guidance. Beyond notes, NoteHub 
<truncated 22398 bytes>